Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-03 neurips-20/cvx-flats.tex
ideas toward proof of lemma

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{cc\,dim}}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\spn}{\mathrm{span}}
\newcommand{\propdis}{\mu}
\newcommand{\affhull}{\mathrm{affhull}}

@@

  Each level set is a set of $p$ having the same subgradient of the Bayes risk of $\ell$, e.g. for some $s$, we have $\gamma_r = \{ p : s \in \partial \ellbar (p) \}$.\bo{cite}
  So $\gamma_r \cap \gamma_{r'} = \{ p : s,s' \in \partial \ellbar(p)\}$, for some $s,s'$.
  \bo{TO DO}
\end{proof}

\begin{lemma}\label{lem:set-valued-prop-flats}
	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \relint\simplex$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
	Then for any flat $F$ containing $p$, $F \cap \simplex \subseteq \gamma_r \iff F \cap \simplex \subseteq \gamma_{r'}$.
\end{lemma}
\begin{proof}
  First, we claim \botodo{separate into another lemma?} that $\gamma_r \cap \gamma_{r'}$ is a closed convex subset of a hyperplane that weakly separates $\gamma_r$ and $\gamma_{r'}$.
  Let it be parameterized by the unit vector $v \in \reals^{\Y}$, where $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0 \}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0\}$, and $q \in \gamma_r \cap \gamma_{r'} \implies v \cdot q = 0$.

>>>>

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{cc\,dim}}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\spn}{\mathrm{span}}
\newcommand{\propdis}{\mu}
\newcommand{\affhull}{\mathrm{affhull}}
\newcommand{\epi}{\mathrm{epi}}

@@

  \bo{Not finished - Sketch next. I don't know if we can appeal to something, but here's my approach to proceed.}

  \bo{Approach 1}

  Each level set corresponds to a report $r$, which corresponds to a supporting hyperplane $h_r$ of the epigraph of the Bayes risk, where $\gamma_r$ is the set of points above which $h_r$ supports $\epi(\ellbar)$.\bo{cite...?}
  So $\gamma_r \cap \gamma_{r'}$ is the set of points at which both $h_r$ and $h_{r'}$ support $\epi(\ellbar)$.
  \bo{Idea: use properties of hyperplanes from here...not sure how exactly}

  \bo{Approach 2}

  First, we claim $\gamma_r$ and $\gamma_{r'}$ are either equal, or have disjoint relative interiors. \bo{True?}

  If not equal, then the intersection is on the relative boundary of both of them, which since they're convex should give a weakly separating hyperplane.
\end{proof}

\begin{lemma}\label{lem:set-valued-prop-flats}
	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \relint\simplex$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
	Then for any flat $F$ containing $p$, $F \cap \simplex \subseteq \gamma_r \iff F \cap \simplex \subseteq \gamma_{r'}$.
\end{lemma}
\begin{proof}
  First, by Lemma \ref{lem:intersect-levelsets}, $\gamma_r \cap \gamma_{r'}$ is a closed convex subset of a hyperplane that weakly separates $\gamma_r$ and $\gamma_{r'}$.
  Let it be parameterized by the unit vector $v \in \reals^{\Y}$, where $\gamma_r \subseteq \{ q \in \simplex : v \cdot q \leq 0 \}$, while $\gamma_{r'} \subseteq \{ q \in \simplex : v \cdot q \geq 0\}$, and $q \in \gamma_r \cap \gamma_{r'} \implies v \cdot q = 0$.
